Analysis and results

### 2023-05-19 analysis/03_analysis.Rmd
Attempting an mnl-index model

# Load data and design
data <- read_rds(here::here("data", "derived_data", "data.rds"))
X <- read_rds(here::here("data", "derived_data", "mnl_dummy_design.rds"))
if (interactions == 1) X <- read_rds(here::here("data", "derived_data", "mnl_dummy_interactions.rds"))

@@

# Run the model and save data and model output
fit <- stan(
  file = here::here("src", "stan_files", "mnl.stan"),
  data = data_list,
  iter = 10000,
  thin = 5,
  seed = 1234
)
run <- list(data = data_list, fit = fit)
write_rds(run, here::here("data", "raw_data", "model_runs", "mnl.rds"))
if (interactions == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "mnl_interactions.rds"))

# Save draws
write_rds(draws, here::here("data", "raw_data", "posterior_draws", "mnl.rds"))
if (interactions == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "mnl_interactions.rds"))
```

>>>>

# Load data and design
data <- read_rds(here::here("data", "derived_data", "data.rds"))
# X <- read_rds(here::here("data", "derived_data", "mnl_dummy_design.rds"))
X <- read_rds(here::here("data", "derived_data", "mnl_index_design.rds"))
if (interactions == 1) X <- read_rds(here::here("data", "derived_data", "mnl_dummy_interactions.rds"))

@@

# Run the model and save data and model output
fit <- stan(
  file = here::here("src", "stan_files", "mnl.stan"),
  data = data_list,
  iter = 10000,
  thin = 5,
  seed = 1234
)
run <- list(data = data_list, fit = fit)
# write_rds(run, here::here("data", "raw_data", "model_runs", "mnl.rds"))
write_rds(run, here::here("data", "raw_data", "model_runs", "mnl_index.rds"))
if (interactions == 1) write_rds(run, here::here("data", "raw_data", "model_runs", "mnl_interactions.rds"))

# Extract and save posterior draws
draws <- fit %>% 
  spread_draws(beta[l]) %>% 
  ungroup() %>% 
  filter(.iteration > 500)

# Save draws
# write_rds(draws, here::here("data", "raw_data", "posterior_draws", "mnl.rds"))
write_rds(draws, here::here("data", "raw_data", "posterior_draws", "mnl_index.rds"))
if (interactions == 1) write_rds(draws, here::here("data", "raw_data", "posterior_draws", "mnl_interactions.rds"))
```
